\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}

### 2020-10-20 arxiv_full_version/main.tex
add acknowledgement

%\usepackage[nonatbib]{neurips_2020}

@@

@@

%\setlength{\parskip}{0.3em}

%\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
\title{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}
\usepackage{authblk}
\author[$\dagger$]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
\author[$\ddagger$]{Fan Yang\samethanks}
\author[$\mathsection$]{Sen Wu}
\author[$\ddagger$]{Weijie S. Su}
\author[$\mathsection$]{Christopher R\'e}
\affil[$\dagger$]{Khoury College of Computer Sciences, Northeastern University}
\affil[$\ddagger$]{Department of Statistics, Wharton School, University of Pennsylvania}
\affil[$\mathsection$]{Department of Computer Science, Stanford University}

\begin{document}
\maketitle

\input{intro}
\input{setup}
%\input{examples}
\input{same_cov}
\input{diff_cov}
%\input{extensions}
%\input{algorithm}
\input{experiments}
\input{experiments_text}
\input{conclusions}
\bibliographystyle{plainnat}
\bibliography{rf,ref_mtl}
\appendix

>>>>

@@

\usepackage{dsfont}

@@

\usepackage{authblk}

\begin{document}

\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
\vspace{0.15in}
\author[1]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
\author[2]{Fan Yang\samethanks}
\author[3]{Sen Wu}
\author[2]{Weijie S. Su}
\author[3]{Christopher R\'e}
\vspace{0.15in}
\affil[1]{Khoury College of Computer Sciences, Northeastern University}
\affil[2]{Department of Statistics, Wharton School, University of Pennsylvania}
\affil[3]{Department of Computer Science, Stanford University}

\maketitle

\input{intro}
\input{setup}
%\input{examples}
\input{same_cov}
\input{diff_cov}
%\input{extensions}
%\input{algorithm}
\input{experiments}
\input{experiments_text}
\input{conclusions}

\subsection*{Acknowledgements:}
Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
HZ and SW's contributions were in part supported by Wharton Dean's Fund for Postdoctoral Research.

\bibliographystyle{plainnat}
\bibliography{rf,ref_mtl}
\appendix
